\documentclass[10pt]{article}

% This is a helpful package that puts math inside length specifications
\usepackage{calc}

% Change font
\usepackage{fouriernc}

% Simpler bibsection for CV sections
\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newenvironment{bibsection}%
        {\vspace{-\baselineskip}\begin{list}{}{%
       \setlength{\leftmargin}{\bibhang}%
       \setlength{\itemindent}{-\leftmargin}%
       \setlength{\itemsep}{\bibsep}%
       \setlength{\parsep}{\z@}%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}
\makeatother

% Layout: Puts the section titles on left side of page
\reversemarginpar

%
%         PAPER SIZE, PAGE NUMBER, AND DOCUMENT LAYOUT NOTES:
%
% The next \usepackage line changes the layout for CV style section
% headings as marginal notes. It also sets up the paper size as either
% letter or A4. By default, letter was used. If A4 paper is desired,
% comment out the letterpaper lines and uncomment the a4paper lines.
%
% As you can see, the margin widths and section title widths can be
% easily adjusted.
%
% ALSO: Notice that the includefoot option can be commented OUT in order
% to put the PAGE NUMBER *IN* the bottom margin. This will make the
% effective text area larger.
%
% IF YOU WISH TO REMOVE PAGE NUMBERS, be sure that the includefoot line
% is uncommented and ALSO uncomment the \pagestyle{empty} a few lines
% below.
%

%% Use these lines for letter-sized paper
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=1.2in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1in,               % 1 inch margins
            includemp]{geometry}

%% Use these lines for A4-sized paper
%\usepackage[paper=a4paper,
%            %includefoot, % Uncomment to put page number above margin
%            marginparwidth=30.5mm,    % Length of section titles
%            marginparsep=1.5mm,       % Space between titles and text
%            margin=25mm,              % 25mm margins
%            includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

%% This gives us fun enumeration environments. compactitem will be nice.
\usepackage{paralist}
\usepackage{fancyhdr}
\pagestyle{fancy}
%\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
%                    \arabic{page} of \protect\pageref*{LastPage} % +LP
                    \arabic{page}                               % -LP
                    \hfill \,}}

% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

%%%%%%%%%%%%%%%%%%%%%%%% End Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%% Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The title (name) with a horizontal rule under it
%
% Usage: \makeheading{name}
%
% Place at top of document. It should be the first thing.
\newcommand{\makeheading}[1]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
                {\large \bfseries #1}\\[-0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}

% The section headings
%
% Usage: \section{section name}
%
% Follow this section IMMEDIATELY with the first line of the section
% text. Do not put whitespace in between. That is, do this:
%
%       \section{My Information}
%       Here is my information.
%
% and NOT this:
%
%       \section{My Information}
%
%       Here is my information.
%
% Otherwise the top of the section header will not line up with the top
% of the section. Of course, using a single comment character (%) on
% empty lines allows for the function of the first example with the
% readability of the second example.
\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}%
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \hspace{0in}%
         \marginpar{
         \raggedright \scshape #1}#2}

% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1]}{\end{itemize}%
         \vspace{-.6\baselineskip}}

% An environment IDENTICAL to outerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactitem}[#1]}{\end{compactitem}}

% An environment IDENTICAL to innerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{loneinnerlist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{compactitem}[#1]}
        {\end{compactitem}\vspace{-.6\baselineskip}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\blankline}{\quad\pagebreak[2]}

% Uses hyperref to link DOI
\newcommand\doilink[1]{\href{http://dx.doi.org/#1}{#1}}
\newcommand\doi[1]{doi:\doilink{#1}}


%%%%%%%%%%%%%%%%%%%%%%%% End Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\makeheading{Samuel Robert Mathias}

\section{Contact Information}
%
\newlength{\rcollength}\setlength{\rcollength}{2.5in}
\begin{tabular}[t]{@{}p{\textwidth-\rcollength}p{\rcollength}}
1 Autumn Street, Room 103 & \\
Boston, MA 02215 & \\
\textit{Phone:} +1 (860) 816 4308 \\
\textit{Email:} \href{mailto:samuel.mathias@childrens.harvard.edu}{samuel.mathias@childrens.harvard.edu}\\
\end{tabular}\\

\section{Academic Appointments}
\begin{bibsection}
\item \href{https://psych.hms.harvard.edu/}{Department of Psychiatry},  \href{https://hms.harvard.edu/}{Harvard Medical School}, Boston, MA
\begin{outerlist}
\item[]\emph{Instructor} \hfill{Nov. 2018 -- present}
\begin{innerlist}
\item Joint appointment with \href{http://www.childrenshospital.org/}{Boston Children's Hospital}
\end{innerlist}
\end{outerlist}
\item \href{https://medicine.yale.edu/psychiatry/}{Department of Psychiatry}, \href{https://medicine.yale.edu/}{Yale School of Medicine}, New Haven, CT
\begin{outerlist}
\item[]\emph{Associate Research Scientist} \hfill{Mar. 2016 -- Nov. 2018}
\begin{innerlist}
\item Mentor: David C.~Glahn
\end{innerlist}
\item[]\emph{Postdoctoral Associate} \hfill{Mar. 2014 -- Feb. 2016}
\begin{innerlist}
\item Mentor: David C.~Glahn
\end{innerlist}
\end{outerlist}
\item CompNet, \href{https://www.bu.edu/}{Boston University,} Boston, MA
\begin{outerlist}
\item[]\emph{Postdoctoral Associate}\hfill{Oct. 2012 -- Feb. 2014}
\begin{innerlist}
\item Mentor: Barbara G.~Shinn-Cunningham
\end{innerlist}
\end{outerlist}
\item \href{https://www.mpg.de/149614/kognition_neuro}{Max Planck Institute for Human Cognitive and Brain Sciences,} Leipzig, Germany
\begin{outerlist}
\item[] \emph{Postdoctoral Associate} \hfill{Dec. 2010 -- Aug. 2012}
\begin{innerlist}
\item Mentor: Katharina von Kriegstein
\end{innerlist}
\end{outerlist}
\end{bibsection}

\section{Hospital Appointments}
\begin{bibsection}
\item \href{http://www.childrenshospital.org/centers-and-services/departments/psychiatry}{Department of Psychiatry}, Boston Children's Hospital, Boston, MA
\begin{outerlist}
\item[]\emph{Research Associate} \hfill{Nov. 2018 -- present}
\begin{innerlist}
\item Joint appointment with Harvard Medical School\\
\end{innerlist}
\end{outerlist}
\end{bibsection}

\section{Education}
\begin{bibsection}
\item \href{http://www.york.ac.uk/psychology/}{University of York}, York, UK
\begin{outerlist}
\item[] PhD in Psychology \hfill{Oct. 2007 -- Nov. 2010} 
\item[] MSc in Cognitive Neuroscience (distinction) \hfill{Oct. 2006 -- Jul. 2007}
\item[] BSc (Hons) in Psychology (2:1 $\approx$ magna cum laude) \hfill{Oct. 2003 -- Jul. 2006}\\
\end{outerlist}
\end{bibsection}

\section{Awards}
\begin{bibsection}
\item \href{http://www.childrenshospital.org/research/centers-departmental-programs/tommy-fuss-center/funded-research-projects/tommy-fuss-center-research-grant-program}{Fuss} Young Investigator Award, sole winner (\$75,000) \hfill{Oct. 2020 -- Sep. 2022}
\item \href{http://www.uni-leipzig.de/~acn/}{ACN} Travel Award (\texteuro 800, declined) \hfill{Apr. 2014}
\item \href{http://www.uni-leipzig.de/~acn/}{ACN} Erasmus Mundus Grant (\texteuro 11,450) \hfill{Dec. 2011}
\item K.~M.~Scott PhD prize, sole winner (\textsterling 350) \hfill{Nov. 2011}
\item Grindley Grant, \href{http://www.eps.ac.uk/}{Experimental Psychology Society} (\textsterling 500) \hfill{Feb. 2010}
\item Travel Award, guarantors of \emph{\href{http://brain.oxfordjournals.org/}{Brain}} (\textsterling 400) \hfill{Feb. 2010}
\item \href{http://www.bbsrc.ac.uk/}{BBSRC} PhD studentship (\textsterling 36,000)  \hfill{Oct. 2007 -- Nov. 2010} 
\item University of York departmental MSc studentship, sole winner ($\sim$\textsterling 3,000) \hfill{Oct. 2006}
\item \href{http://research.microsoft.com/en-us/}{Microsoft Research} Undergraduate Project Prize, sole winner (\textsterling 250) \hfill{Jul. 2006}\\
\end{bibsection}

\section{Researcher Statistics}
\begin{bibsection}
\item h-index: 16 (via \href{https://scholar.google.com/citations?user=fRRZs_4AAAAJ&hl=en}{Google Scholar})
\item Publications: 53 total, 12 first-author
\end{bibsection}

\section{Publications}
\begin{bibsection}

\item \textbf{Mathias, S. R.}, Varghese, L.,  Micheyl, C., \& Shinn-Cunningham, B. G. (2020c). Gradual decay and sudden death of short-term memory for pitch \emph{The Journal of the Acoustical Society of America}, in press.

\item Writing Committee for the ENIGMA-CNV Working Group, van der Meer, D., Sønderby, I. E., Kaufmann, T., Walters, G. B., Abdellaoui, A., Ames, D., Amunts, K., Andersson, M., Armstrong, N. J., Bernard, M., Blackburn, N. B., Blangero, J., Boomsma, D. I., Brodaty, H., Brouwer, R. M., Bülow, R., Cahn, W., Calhoun, V. D., Caspers, S., Cavalleri, G. L., Ching, C. R. K., Cichon, S., Ciufolini, S., Corvin, A., Crespo-Facorro, B., Curran, J. E., Dalvie, S., Dazzan, P., de Geus, E. J. C., de Zubicaray, G. I., de Zwarte, S. M. C., Delanty, N., den Braber, A., Desrivieres, S., Di Forti, M., Doherty, J. L., Donohoe, G., Ehrlich, S., Eising, E., Espeseth, T., Fisher, S. E., Fladby, T., Frei, O., Frouin, V., Fukunaga, M., Gareau, T., Glahn, D. C., Grabe, H. J., Groenewold, N. A., Gústafsson, Ó., Haavik, J., Haberg, A. K., Hashimoto, R., Hehir-Kwa, J. Y., Hibar, D. P., Hillegers, M. H. J., Hoffmann, P., Holleran, L., Hottenga, J. J., Hulshoff Pol, H. E., Ikeda, M., Jacquemont, S., Jahanshad, N., Jockwitz, C., Johansson, S., Jönsson, E. G., Kikuchi, M., Knowles, E. E. M., Kwok, J. B., Le Hellard, S., Linden, D. E. J., Liu, J., Lundervold, A., Lundervold, A. J., Martin, N. G., Mather, K. A., \textbf{Mathias, S. R.}, McMahon, K. L., McRae, A. F., Medland, S. E., Moberget, T., Moreau, C., Morris, D. W., Mühleisen, T. W., Murray, R. M., Nordvik, J. E., Nyberg, L., Olde Loohuis, L. M., Ophoff, R. A., Owen, M. J., Paus, T., Pausova, Z., Peralta, J. M., Pike, B., Prieto, C., Quinlan, E. B., Reinbold, C. S., Reis Marques, T., Rucker, J. J. H., Sachdev, P. S., Sando, S. B., Schofield, P. R., Schork, A. J., Schumann, G., Shin, J., Shumskaya, E., Silva, A. I., Sisodiya, S. M., Steen, V. M., Stein, D. J., Strike, L. T., Tamnes, C. K., Teumer, A., Thalamuthu, A., Tordesillas-Gutiérrez, D., Uhlmann, A., Úlfarsson, M. Ö., van 't Ent, D., van den Bree, M. B. M., Vassos, E., Wen, W., Wittfeld, K., Wright, M. J., Zayats, T., Dale, A. M., Djurovic, S., Agartz, I., Westlye, L. T., Stefánsson, H., Stefánsson, K., Thompson, P. M., \& Andreassen, O. A. (2020). 1q21.1 distal copy number variants are associated with cerebral and cognitive alterations in humans. \emph{Translational Psychiatry}, in press.

\item Koenis, M., Mastrovito, D., Esteban, E., Durnez, J., Alexander-Bloch, A., Knowles, E., \textbf{Mathias, S.}, Mollon, J., Pearlson, G., Frangou, S., Blangero, J., Poldrack, R., \& Glahn, D. (2020). Associations of cannabis use disorder with cognition, brain structure, and brain function in African Americans. \emph{Human Brain Mapping}, in press.

\item Rodrigue, A. L., Mastrovito, D., Esteban, E., Durnez, J., Koenis, M., Alexander-Bloch, A., Knowles, E., \textbf{Mathias, S.}, Mollon, J., Pearlson, G., Frangou, S., Blangero, J., Poldrack, R., \& Glahn, D. (2020). Searching for imaging biomarkers using psychotic dysconnectivity. \emph{Biological Psychiatry: Cognitive Neuroscience and Neuroimaging}, in press.

\item Pizzagalli, F., Auzias, G., Yang, Q.,  \textbf{Mathias, S. R.}, Faskowitz, J., Boyd, J. D., Amini, A., Rivi\'ere, D., McMahon, K. L., de Zubicaray, G. I., Martin, N. G., Mangin, J. F., Glahn, D. C., Blangero, J., Wright, M. J., Thompson, P. M., Kochunov, P., \& Jahanshad, N. (2020). The reliability and heritability of cortical folds and their genetic correlations across hemispheres. \emph{Communications Biology}, \emph{3}(1), 510. DOI:~\href{https://doi.org/10.1038/s42003-020-01163-1}{10.1038/s42003-020-01163-1}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=32934300}{32934300}.

\item Alexander-Bloch, A. F., Raznahan, A., Shinohara, R. T., \textbf{Mathias, S. R.}, Bathulapalli, H., Bhalla, I. P., Goulet, J. L., Satterthwaite, T. D., Bassett, D. S., Glahn, D. C., \& Brandt, C. A. (2020). The architecture of co-morbidity networks of physical and mental health conditions in military veterans. \emph{Proceedings: Mathematical, Physical, and Engineering Sciences}, \emph{476}(2239), 20190790. DOI:~\href{https://doi.org/10.1098/rspa.2019.0790}{10.1098/rspa.2019.0790}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=32831602}{32831602}.

\item Rodrigue, A. L., Alexander-Bloch, A. F., Knowles, E. E. M., \textbf{Mathias, S. R.}, Mollon, J., Koenis, M. M. G., Perrone-Bizzozero, N. I., Almasy, L., Turner, J. A., Calhoun, V. D., \& Glahn, D. C. (2020). Genetic contributions to multivariate data-driven brain networks constructed via source-based morphometry. \emph{Cerebral Cortex}, \emph{30}(9), 4899--4913. DOI:~\href{https://doi.org/10.1093/cercor/bhaa082}{10.1093/cercor/bhaa082}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=32318716}{32318716}.

\item Mollon, J., Curran J. E., \textbf{Mathias, S. R.}, Knowles, E. E. M., Carlile, P., Fox, P. T., Olvera, R. L., G\"oring, H. H. H., Rodrigue, A., Almasy, L., Duggirala, R., Blangero, J. \& Glahn, D. C. (2020). Neurocognitive impairment in Type 2 Diabetes: Evidence for shared genetic etiology. \emph{Diabetologia}, \emph{63}(5), 977--986. DOI:~\href{https://doi.org/10.1007/s00125-020-05101-y}{10.1007/s00125-020-05101-y}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=32016567}{32016567}.

\item \textbf{Mathias, S. R.}, Knowles, E. E. M., Mollon, J., Rodrigue, A., Koenis, M. M. C., Alexander-Bloch, A. F., Winkler, A. M., Olvera, R. L., Duggirala, R., G\"oring, H. H., Curran J. E., Fox, P. T., Almasy, L., Blangero, J. \& Glahn, D. C. (2020b). Minimal relationship between brain gyrification and general cognitive ability in humans. \emph{Cerebral Cortex}. DOI:~\href{https://doi.org/10.1093/cercor/bhz319}{10.1093/cercor/bhz319}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=32037459}{32037459}.

\item Kong, X. Z., Postema, M. C., Guadalupe, T., de Kovel, C., Boedhoe, P. S. W., Hoogman, M., \textbf{Mathias, S. R.}, van Rooij, D., Schijven, D., Glahn, D. C., Medland, S. E., Jahanshad, N., Thomopoulos, S. I., Turner, J. A., Buitelaar, J., van Erp, T. G. M., Franke, B., Fisher, S. E., van den Heuvel, O. A., Schmaal, L., Thompson, P. M., \& Francks, C. (2020). Mapping brain asymmetry in health and disease through the ENIGMA consortium. \emph{Human Brain Mapping}. DOI:~\href{https://doi.org/10.1002/hbm.25033}{10.1002/hbm.25033}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=32420672}{32420672}.

\item Writing Committee for the ENIGMA-CNV Working Group, van der Meer, D., Sønderby, I. E., Kaufmann, T., Walters, G. B., Abdellaoui, A., Ames, D., Amunts, K., Andersson, M., Armstrong, N. J., Bernard, M., Blackburn, N. B., Blangero, J., Boomsma, D. I., Brodaty, H., Brouwer, R. M., Bülow, R., Cahn, W., Calhoun, V. D., Caspers, S., Cavalleri, G. L., Ching, C. R. K., Cichon, S., Ciufolini, S., Corvin, A., Crespo-Facorro, B., Curran, J. E., Dalvie, S., Dazzan, P., de Geus, E. J. C., de Zubicaray, G. I., de Zwarte, S. M. C., Delanty, N., den Braber, A., Desrivieres, S., Di Forti, M., Doherty, J. L., Donohoe, G., Ehrlich, S., Eising, E., Espeseth, T., Fisher, S. E., Fladby, T., Frei, O., Frouin, V., Fukunaga, M., Gareau, T., Glahn, D. C., Grabe, H. J., Groenewold, N. A., Gústafsson, Ó., Haavik, J., Haberg, A. K., Hashimoto, R., Hehir-Kwa, J. Y., Hibar, D. P., Hillegers, M. H. J., Hoffmann, P., Holleran, L., Hottenga, J. J., Hulshoff Pol, H. E., Ikeda, M., Jacquemont, S., Jahanshad, N., Jockwitz, C., Johansson, S., Jönsson, E. G., Kikuchi, M., Knowles, E. E. M., Kwok, J. B., Le Hellard, S., Linden, D. E. J., Liu, J., Lundervold, A., Lundervold, A. J., Martin, N. G., Mather, K. A., \textbf{Mathias, S. R.}, McMahon, K. L., McRae, A. F., Medland, S. E., Moberget, T., Moreau, C., Morris, D. W., Mühleisen, T. W., Murray, R. M., Nordvik, J. E., Nyberg, L., Olde Loohuis, L. M., Ophoff, R. A., Owen, M. J., Paus, T., Pausova, Z., Peralta, J. M., Pike, B., Prieto, C., Quinlan, E. B., Reinbold, C. S., Reis Marques, T., Rucker, J. J. H., Sachdev, P. S., Sando, S. B., Schofield, P. R., Schork, A. J., Schumann, G., Shin, J., Shumskaya, E., Silva, A. I., Sisodiya, S. M., Steen, V. M., Stein, D. J., Strike, L. T., Tamnes, C. K., Teumer, A., Thalamuthu, A., Tordesillas-Gutiérrez, D., Uhlmann, A., Úlfarsson, M. Ö., van 't Ent, D., van den Bree, M. B. M., Vassos, E., Wen, W., Wittfeld, K., Wright, M. J., Zayats, T., Dale, A. M., Djurovic, S., Agartz, I., Westlye, L. T., Stefánsson, H., Stefánsson, K., Thompson, P. M., \& Andreassen, O. A. (2020). Association of copy number variation of the 15q11.2 bp1-bp2 region with cortical and subcortical morphology and cognition. \emph{JAMA Psychiatry}, \emph{77}(4), 420--430. DOI:~\href{https://doi.org/10.1001/jamapsychiatry.2019.3779}{10.1001/jamapsychiatry.2019.3779}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=31665216}{31665216}.

\item Grasby, K. L., Jahanshad, N., Painter, J. N., Colodro-Conde, L., Bralten, J., Hibar, D. P., Lind, P. A., Pizzagalli, F., Ching, C. R. K., McMahon, M. A. B., Shatokhina, N., Zsembik, L. C. P., Thomopoulos, S. I., Zhu, A. H., Strike, L. T., Agartz, I., Alhusaini, S., Almeida, M. A. A., Alnæs, D., Amlien, I. K., Andersson, M., Ard, T., Armstrong, N. J., Ashley-Koch, A., Atkins, J. R., Bernard, M., Brouwer, R. M., Buimer, E. E. L., Bülow, R., Bürger, C., Cannon, D. M., Chakravarty, M., Chen, Q., Cheung, J. W., Couvy-Duchesne, B., Dale, A. M., Dalvie, S., de Araujo, T. K., de Zubicaray, G. I., de Zwarte, S. M. C., den Braber, A., Doan, N. T., Dohm, K., Ehrlich, S., Engelbrecht, H. R., Erk, S., Fan, C. C., Fedko, I. O., Foley, S. F., Ford, J. M., Fukunaga, M., Garrett, M. E., Ge, T., Giddaluru, S., Goldman, A. L., Green, M. J., Groenewold, N. A., Grotegerd, D., Gurholt, T. P., Gutman, B. A., Hansell, N. K., Harris, M. A., Harrison, M. B., Haswell, C. C., Hauser, M., Herms, S., Heslenfeld, D. J., Ho, N. F., Hoehn, D., Hoffmann, P., Holleran, L., Hoogman, M., Hottenga, J. J., Ikeda, M., Janowitz, D., Jansen, I. E., Jia, T., Jockwitz, C., Kanai, R., Karama, S., Kasperaviciute, D., Kaufmann, T., Kelly, S., Kikuchi, M., Klein, M., Knapp, M., Knodt, A. R., Krämer, B., Lam, M., Lancaster, T. M., Lee, P. H., Lett, T. A., Lewis, L. B., Lopes-Cendes, I., Luciano, M., Macciardi, F., Marquand, A. F., \textbf{Mathias, S. R.}, Melzer, T. R., Milaneschi, Y., Mirza-Schreiber, N., Moreira, J. C. V., Mühleisen, T. W., Müller-Myhsok, B., Najt, P., Nakahara, S., Nho, K., Olde Loohuis, L. M., Orfanos, D. P., Pearson, J. F., Pitcher, T. L., Pütz, B., Quidé, Y., Ragothaman, A., Rashid, F. M., Reay, W. R., Redlich, R., Reinbold, C. S., Repple, J., Richard, G., Riedel, B. C., Risacher, S. L., Rocha, C. S., Mota, N. R., Salminen, L., Saremi, A., Saykin, A. J., Schlag, F., Schmaal, L., Schofield, P. R., Secolin, R., Shapland, C. Y., Shen, L., Shin, J., Shumskaya, E., Sønderby, I. E., Sprooten, E., Tansey, K. E., Teumer, A., Thalamuthu, A., Tordesillas-Gutiérrez, D., Turner, J. A., Uhlmann, A., Vallerga, C. L., van der Meer, D., van Donkelaar, M. M. J., van Eijk, L., van Erp, T. G. M., van Haren, N. E. M., van Rooij, D., van Tol, M. J., Veldink, J. H., Verhoef, E., Walton, E., Wang, M., Wang, Y., Wardlaw, J. M., Wen, W., Westlye, L. T., Whelan, C. D., Witt, S. H., Wittfeld, K., Wolf, C., Wolfers, T., Wu, J. Q., Yasuda, C. L., Zaremba, D., Zhang, Z., Zwiers, M. P., Artiges, E., Assareh, A. A., Ayesa-Arriola, R., Belger, A., Brandt, C. L., Brown, G. G., Cichon, S., Curran, J. E., Davies, G. E., Degenhardt, F., Dennis, M. F., Dietsche, B., Djurovic, S., Doherty, C. P., Espiritu, R., Garijo, D., Gil, Y., Gowland, P. A., Green, R. C., Häusler, A. N., Heindel, W., Ho, B. C., Hoffmann, W. U., Holsboer, F., Homuth, G., Hosten, N., Jack, C. R., Jang, M., Jansen, A., Kimbrel, N. A., Kolskår, K., Koops, S., Krug, A., Lim, K. O., Luykx, J. J., Mathalon, D. H., Mather, K. A., Mattay, V. S., Matthews, S., Mayoral Van Son, J., McEwen, S. C., Melle, I., Morris, D. W., Mueller, B. A., Nauck, M., Nordvik, J. E., Nöthen, M. M., O'Leary, D. S., Opel, N., Martinot, M. P., Pike, G. B., Preda, A., Quinlan, E. B., Rasser, P. E., Ratnakar, V., Reppermund, S., Steen, V. M., Tooney, P. A., Torres, F. R., Veltman, D. J., Voyvodic, J. T., Whelan, R., White, T., Yamamori, H., Adams, H. H. H., Bis, J. C., Debette, S., Decarli, C., Fornage, M., Gudnason, V., Hofer, E., Ikram, M. A., Launer, L., Longstreth, W. T., Lopez, O. L., Mazoyer, B., Mosley, T. H., Roshchupkin, G. V., Satizabal, C. L., Schmidt, R., Seshadri, S., Yang, Q., Alzheimer’s Disease Neuroimaging Initiative, CHARGE Consortium, EPIGEN Consortium, IMAGEN Consortium, SYS Consortium, Parkinson’s Progression Markers Initiative, Alvim, M. K. M., Ames, D., Anderson, T. J., Andreassen, O. A., Arias-Vasquez, A., Bastin, M. E., Baune, B. T., Beckham, J. C., Blangero, J., Boomsma, D. I., Brodaty, H., Brunner, H. G., Buckner, R. L., Buitelaar, J. K., Bustillo, J. R., Cahn, W., Cairns, M. J., Calhoun, V., Carr, V. J., Caseras, X., Caspers, S., Cavalleri, G. L., Cendes, F., Corvin, A., Crespo-Facorro, B., Dalrymple-Alford, J. C., Dannlowski, U., de Geus, E. J. C., Deary, I. J., Delanty, N., Depondt, C., Desrivières, S., Donohoe, G., Espeseth, T., Fernández, G., Fisher, S. E., Flor, H., Forstner, A. J., Francks, C., Franke, B., Glahn, D. C., Gollub, R. L., Grabe, H. J., Gruber, O., Håberg, A. K., Hariri, A. R., Hartman, C. A., Hashimoto, R., Heinz, A., Henskens, F. A., Hillegers, M. H. J., Hoekstra, P. J., Holmes, A. J., Hong, L. E., Hopkins, W. D., Hulshoff Pol, H. E., Jernigan, T. L., Jönsson, E. G., Kahn, R. S., Kennedy, M. A., Kircher, T. T. J., Kochunov, P., Kwok, J. B. J., Le Hellard, S., Loughland, C. M., Martin, N. G., Martinot, J. L., McDonald, C., McMahon, K. L., Meyer-Lindenberg, A., Michie, P. T., Morey, R. A., Mowry, B., Nyberg, L., Oosterlaan, J., Ophoff, R. A., Pantelis, C., Paus, T., Pausova, Z., Penninx, B. W. J. H., Polderman, T. J. C., Posthuma, D., Rietschel, M., Roffman, J. L., Rowland, L. M., Sachdev, P. S., Sämann, P. G., Schall, U., Schumann, G., Scott, R. J., Sim, K., Sisodiya, S. M., Smoller, J. W., Sommer, I. E., St Pourcain, B., Stein, D. J., Toga, A. W., Trollor, J. N., Van der Wee, N. J. A., van 't Ent, D., Völzke, H., Walter, H., Weber, B., Weinberger, D. R., Wright, M. J., Zhou, J., Stein, J. L., Thompson, P. M., Medland, S. E., \& Enhancing NeuroImaging Genetics through Meta-Analysis Consortium (ENIGMA)—Genetics working group (2020). The genetic architecture of the human cerebral cortex. \emph{Science}, \emph{367}(6484). DOI:~\href{https://doi.org/10.1126/science.aay6690}{10.1126/science.aay6690}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=32193296}{32193296}.

\item Alexander-Bloch, A. F., Raznahan, A., Vandekar, S. N., Seidlitz, J., Lu, Z., \textbf{Mathias, S. R.}, Knowles, E., Mollon, J., Rodrigue, A., Curran, J. E., Görring, H. H. H., Satterthwaite, T. D., Gur, R. E., Bassett, D. S., Hoftman, G. D., Pearlson, G., Shinohara, R. T., Liu, S., Fox, P. T., Almasy, L., Blangero, J., \& Glahn, D. C. (2020). Imaging local genetic influences on cortical folding. \emph{Proceedings of the National Academy of Sciences of the United States of America}, \emph{117}(13), 7430--7436. DOI:~\href{https://doi.org/10.1073/pnas.1912064117}{10.1073/pnas.1912064117}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=32170019}{32170019}.

\item Sønderby, I. E., Gústafsson, Ó., Doan, N. T., Hibar, D. P., Martin-Brevet, S., Abdellaoui, A., Ames, D., Amunts, K., Andersson, M., Armstrong, N. J., Bernard, M., Blackburn, N., Blangero, J., Boomsma, D. I., Bralten, J., Brattbak, H. R., Brodaty, H., Brouwer, R. M., Bülow, R., Calhoun, V., Caspers, S., Cavalleri, G., Chen, C. H., Cichon, S., Ciufolini, S., Corvin, A., Crespo-Facorro, B., Curran, J. E., Dale, A. M., Dalvie, S., Dazzan, P., de Geus, E. J. C., de Zubicaray, G. I., de Zwarte, S. M. C., Delanty, N., den Braber, A., Desrivières, S., Donohoe, G., Draganski, B., Ehrlich, S., Espeseth, T., Fisher, S. E., Franke, B., Frouin, V., Fukunaga, M., Gareau, T., Glahn, D. C., Grabe, H., Groenewold, N. A., Haavik, J., Håberg, A., Hashimoto, R., Hehir-Kwa, J. Y., Heinz, A., Hillegers, M. H. J., Hoffmann, P., Holleran, L., Hottenga, J. J., Hulshoff, H. E., Ikeda, M., Jahanshad, N., Jernigan, T., Jockwitz, C., Johansson, S., Jonsdottir, G. A., Jönsson, E. G., Kahn, R., Kaufmann, T., Kelly, S., Kikuchi, M., Knowles, E. E. M., Kolskår, K. K., Kwok, J. B., Hellard, S. L., Leu, C., Liu, J., Lundervold, A. J., Lundervold, A., Martin, N. G., Mather, K., \textbf{Mathias, S. R.}, McCormack, M., McMahon, K. L., McRae, A., Milaneschi, Y., Moreau, C., Morris, D., Mothersill, D., Mühleisen, T. W., Murray, R., Nordvik, J. E., Nyberg, L., Olde Loohuis, L. M., Ophoff, R., Paus, T., Pausova, Z., Penninx, B., Peralta, J. M., Pike, B., Prieto, C., Pudas, S., Quinlan, E., Quintana, D. S., Reinbold, C. S., Marques, T. R., Reymond, A., Richard, G., Rodriguez-Herreros, B., Roiz-Santiañez, R., Rokicki, J., Rucker, J., Sachdev, P., Sanders, A. M., Sando, S. B., Schmaal, L., Schofield, P. R., Schork, A. J., Schumann, G., Shin, J., Shumskaya, E., Sisodiya, S., Steen, V. M., Stein, D. J., Steinberg, S., Strike, L., Teumer, A., Thalamuthu, A., Tordesillas-Gutierrez, D., Turner, J., Ueland, T., Uhlmann, A., Ulfarsson, M. O., van 't Ent, D., van der Meer, D., van Haren, N. E. M., Vaskinn, A., Vassos, E., Walters, G. B., Wang, Y., Wen, W., Whelan, C. D., Wittfeld, K., Wright, M., Yamamori, H., Zayats, T., Agartz, I., Westlye, L. T., Jacquemont, S., Djurovic, S., Stefánsson, H., Stefánsson, K., Thompson, P., Andreassen, O. A., \& 16p11.2 European Consortium, for the ENIGMA-CNV working group (2020). Dose response of the 16p11.2 distal copy number variant on intracranial volume and basal ganglia. \emph{Molecular Psychiatry}, \emph{25}(3), 584--602. DOI:~\href{https://doi.org/10.1038/s41380-018-0118-1}{10.1038/s41380-018-0118-1}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=30283035}{30283035}.

\item \textbf{Mathias, S. R.}, Varghese, L.,  Micheyl, C., \& Shinn-Cunningham, B. G. (2020a). On the utility of perceptual anchors during pure-tone frequency discrimination. \emph{The Journal of the Acoustical Society of America}, \emph{147}(1), 371. 
DOI:~\href{https://doi.org/10.1121/10.0000584}{10.1121/10.0000584}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=32006971}{32006971}.

\item Mollon, J., \textbf{Mathias, S. R.}, Knowles, E. E. M., Rodrigue, A., Koenis, M. M. G., Pearlson, G. D., Reichenberg, A., Barrett, J., Denbow, D., Aberizk, K., Zatony, M., Poldrack, R. A., Blangero, J., \& Glahn, D. C. (2020). Cognitive impairment from early to middle adulthood in patients with affective and nonaffective psychotic disorders. \emph{Psychological Medicine}, \emph{50}(1), 48--57. DOI:~\href{https://doi.org/10.1017/s0033291718003938}{10.1017/s0033291718003938}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=30606277}{30606277}.


\item Rodrigue, A. L., Knowles, E. E., Mollon, J., \textbf{Mathias, S. R.}, Koenis, M. M., Peralta, J. M., Leandro, A. C., Fox, P. T., Sprooten, E., Kochunov, P., Olvera, R. L., Duggirala, R., Almasy, L., Curran, J. E., Blangero, J., \& Glahn, D. C. (2019). Evidence for genetic correlation between human cerebral white matter microstructure and inflammation. \emph{Human Brain Mapping}, \emph{40}(14), 4180--4191. DOI:~DOI:~\href{https://doi.org/10.1002/hbm.24694}{10.1002/hbm.24694}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=31187567}{31187567}.

\item Knowles, E. E. M., Curran, J. E., Göring, H. H. H., \textbf{Mathias, S. R.}, Mollon, J., Rodrigue, A., Olvera, R. L., Leandro, A., Duggirala, R., Almasy, L., Blangero, J., \& Glahn, D. C. (2019). Family-based analyses reveal novel genetic overlap between cytokine interleukin-8 and risk for suicide attempt. \emph{Brain, Behavior, and Immunity}, \emph{80}, 292--299. DOI:~\href{https://doi.org/10.1016/j.bbi.2019.04.004}{10.1016/j.bbi.2019.04.004}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=30953777}{30953777}.

\item Groman, S. M., Massi, B., \textbf{Mathias, S. R.}, Lee, D., \& Taylor, J. R. (2019b). Model-free and model-based influences in addiction-related behaviors. \emph{Biological Psychiatry}, \emph{85}(11), 936--945. DOI:~\href{https://doi.org/10.1016/j.biopsych.2018.12.017}{10.1016/j.biopsych.2018.12.017}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=30737015}{30737015}.

\item \textbf{Mathias, S. R.} \& von Kriegstein, K. (2019). Voice processing and voice-identity recognition. In K. Siedenburg, C. Saitis, S. McAdams, A. Popper, R. Fay (Eds.) \emph{Timbre: Acoustics, perception, and cognition} (Springer handbook of auditory research vol.~69, pp.~175--209). Cham, Switzerland:~Springer. DOI:~\href{https://doi.org/10.1007/978-3-030-14832-4_7}{10.1007/978-3-030-14832-4\_7}.

\item Knowles, E. E. M., \textbf{Mathias, S. R.}, Pearlson, G. D., Barrett, J., Mollon, J., Denbow, D., Aberzik, K., Zatony, M., \& Glahn, D. C. (2019). Clinical correlates of subsyndromal depression in African American individuals with psychosis: the relationship with positive symptoms and comorbid substance dependence. \emph{Schizophrenia Research}, \emph{206}, 333--346. DOI:~\href{https://doi.org/10.1016/j.schres.2018.10.022}{10.1016/j.schres.2018.10.022}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=30482645}{30482645}.
\item Glahn, D. C., Nimgaonkar, V. L., Raventós, H., Contreras, J., McIntosh, A. M., Thomson, P. A., Jablensky, A., McCarthy, N. S., Charlesworth, J. C., Blackburn, N. B., Peralta, J. M., Knowles, E. E. M., \textbf{Mathias, S. R.}, Ament, S. A., McMahon, F. J., Gur, R. C., Bucan, M., Curran, J. E., Almasy, L., Gur, R. E., \& Blangero, J. (2019). Rediscovering the value of families for psychiatric genetics research. \emph{Molecular Psychiatry}, \emph{24}(4), 523--535. DOI:~\href{https://doi.org/10.1038/s41380-018-0073-x}{10.1038/s41380-018-0073-x}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=29955165}{29955165}.

\item Knowles, E. E. M., \textbf{Mathias, S. R.}, Mollon, J., Rodrigue, A., Koenis, M. M. G., Dyer, T. D., Goring, H. H. H., Curran, J. E., Olvera, R. L., Duggirala, R., Almasy, L., Blangero, J., \& Glahn, D. C. (2019). A QTL on chromosome 3q23 influences processing speed in humans. \emph{Genes, Brain, and Behavior}, \emph{18}(4), e12530. DOI:~\href{https://doi.org/10.1111/gbb.12530}{10.1111/gbb.12530}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=30379395}{30379395}.

\item Alexander-Bloch, A. F., \textbf{Mathias, S. R.}, Fox, P. T., Olvera, R. L., Göring, H. H. H., Duggirala, R., Curran, J. E., Blangero, J., \& Glahn, D. C. (2019). Human cortical thickness organized into genetically-determined communities across spatial resolutions. \emph{Cerebral Cortex}, \emph{29}(1), 106--118. DOI:~\href{https://doi.org/10.1093/cercor/bhx309}{10.1093/cercor/bhx309}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=29190330}{29190330}.

\item Groman, S. M., Massi, B., \textbf{Mathias, S. R.}, Curry, D. W., Lee, D., \& Taylor, J. R. (2019a). Neurochemical and behavioral dissections of decision-making in a rodent multistage task. \emph{The Journal of Neuroscience}, \emph{39}(2), 295--306. DOI:~\href{https://doi.org/10.1523/JNEUROSCI.2219-18.2018}{10.1523/JNEUROSCI.2219-18.2018}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=30413646}{30413646}.
\item Knowles, E. E. M., Curran, J. E., Meikle, P. J., Huynh, K., \textbf{Mathias, S. R.}, Göring, H. H. H., VandeBerg, J. L., Mahaney, M. C., Jalbrzikowski, M., Mosior, M. K., Michael, L. F., Olvera, R. L., Duggirala, R., Almasy, L., Glahn, D. C., \& Blangero, J. (2018). Disentangling the genetic overlap between cholesterol and suicide risk. \emph{Neuropsychopharmacology}, \emph{43}(13), 2556--2563. DOI:~\href{https://doi.org/10.1038/s41386-018-0162-1}{10.1038/s41386-018-0162-1}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=30082891}{30082891}.
\item Kreitewolf, J., \textbf{Mathias, S. R.}, Trapeau, R., Obleser, J., \& Schönwiesner, M. (2018). Perceptual grouping in the cocktail party: contributions of voice-feature continuity. \emph{The Journal of the Acoustical Society of America}, \emph{144}(4), 2178. DOI:~\href{https://doi.org/10.1121/1.5058684}{10.1121/1.5058684}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=30404485}{30404485}.
\item Mollon, J., Knowles, E. E. M., \textbf{Mathias, S. R.}, Gur, R., Peralta, J. M., Weiner, D. J., Robinson, E. B., Gur, R. E., Blangero, J., Almasy, L., \& Glahn, D. C. (2018). Genetic influence on cognitive development between childhood and adulthood. \emph{Molecular Psychiatry}. DOI:~\href{https://doi.org/10.1038/s41380-018-0277-0}{10.1038/s41380-018-0277-0}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=30644433}{30644433}.
\item Kong, X. Z., \textbf{Mathias, S. R.}, Guadalupe, T., ENIGMA Laterality Working Group., Glahn, D. C., Franke, B., Crivello, F., Tzourio-Mazoyer, N., Fisher, S. E., Thompson, P. M., \& Francks, C. (2018). Mapping cortical brain asymmetry in 17,141 healthy individuals worldwide via the ENIGMA consortium. \emph{Proceedings of the National Academy of Sciences of the United States of America}, \emph{115}(22), E5154--E5163. DOI:~\href{https://doi.org/10.1073/pnas.1718418115}{10.1073/pnas.1718418115}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=29764998}{29764998}.
\item \textbf{Mathias, S. R.}, Knowles, E. E. M., Barrett, J., Beetham, T., Leach, O., Buccheri, S., Aberizk, K., Blangero, J., Poldrack, R. A., \& Glahn, D. C. (2018). Deficits in visual working-memory capacity and general cognition in African Americans with psychosis. \emph{Schizophrenia Research}, \emph{193}, 100--106. DOI:~\href{https://doi.org/10.1016/j.schres.2017.08.015}{10.1016/j.schres.2017.08.015}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=28843437}{28843437}.
\item Hodgson, K., Poldrack, R. A., Curran, J. E., Knowles, E. E., \textbf{Mathias, S.}, Göring, H. H. H., Yao, N., Olvera, R. L., Fox, P. T., Almasy, L., Duggirala, R., Barch, D. M., Blangero, J., \& Glahn, D. C. (2017). Shared genetic factors influence head motion during MRI and body mass index. \emph{Cerebral Cortex}, \emph{27}(12), 5539--5546. DOI:~\href{https://doi.org/10.1093/cercor/bhw321}{10.1093/cercor/bhw321}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=27744290}{27744290}.
\item Guadalupe, T., \textbf{Mathias, S. R.}, vanErp, T. G. M., Whelan, C. D., Zwiers, M. P., Abe, Y., Abramovic, L., Agartz, I., Andreassen, O. A., Arias-Vásquez, A., Aribisala, B. S., Armstrong, N. J., Arolt, V., Artiges, E., Ayesa-Arriola, R., Baboyan, V. G., Banaschewski, T., Barker, G., Bastin, M. E., Baune, B. T., Blangero, J., Bokde, A. L. W., Boedhoe, P. S. W., Bose, A., Brem, S., Brodaty, H., Bromberg, U., Brooks, S., Büchel, C., Buitelaar, J., Calhoun, V. D., Cannon, D. M., Cattrell, A., Cheng, Y., Conrod, P. J., Conzelmann, A., Corvin, A., Crespo-Facorro, B., Crivello, F., Dannlowski, U., de Zubicaray, G. I., de Zwarte, S. M. C., Deary, I. J., Desrivières, S., Doan, N. T., Donohoe, G., Dørum, E. S., Ehrlich, S., Espeseth, T., Fernández, G., Flor, H., Fouche, J. P., Frouin, V., Fukunaga, M., Gallinat, J., Garavan, H., Gill, M., Suarez, A. G., Gowland, P., Grabe, H. J., Grotegerd, D., Gruber, O., Hagenaars, S., Hashimoto, R., Hauser, T. U., Heinz, A., Hibar, D. P., Hoekstra, P. J., Hoogman, M., Howells, F. M., Hu, H., Hulshoff Pol, H. E., Huyser, C., Ittermann, B., Jahanshad, N., Jönsson, E. G., Jurk, S., Kahn, R. S., Kelly, S., Kraemer, B., Kugel, H., Kwon, J. S., Lemaitre, H., Lesch, K. P., Lochner, C., Luciano, M., Marquand, A. F., Martin, N. G., Martínez-Zalacaín, I., Martinot, J. L., Mataix-Cols, D., Mather, K., McDonald, C., McMahon, K. L., Medland, S. E., Menchón, J. M., Morris, D. W., Mothersill, O., Maniega, S. M., Mwangi, B., Nakamae, T., Nakao, T., Narayanaswaamy, J. C., Nees, F., Nordvik, J. E., Onnink, A. M. H., Opel, N., Ophoff, R., Paillère Martinot, M. L., Papadopoulos Orfanos, D., Pauli, P., Paus, T., Poustka, L., Reddy, J. Y., Renteria, M. E., Roiz-Santiáñez, R., Roos, A., Royle, N. A., Sachdev, P., Sánchez-Juan, P., Schmaal, L., Schumann, G., Shumskaya, E., Smolka, M. N., Soares, J. C., Soriano-Mas, C., Stein, D. J., Strike, L. T., Toro, R., Turner, J. A., Tzourio-Mazoyer, N., Uhlmann, A., Hernández, M. V., van den Heuvel, O. A., van der Meer, D., van Haren, N. E. M., Veltman, D. J., Venkatasubramanian, G., Vetter, N. C., Vuletic, D., Walitza, S., Walter, H., Walton, E., Wang, Z., Wardlaw, J., Wen, W., Westlye, L. T., Whelan, R., Wittfeld, K., Wolfers, T., Wright, M. J., Xu, J., Xu, X., Yun, J. Y., Zhao, J., Franke, B., Thompson, P. M., Glahn, D. C., Mazoyer, B., Fisher, S. E., \& Francks, C. (2017). Human subcortical brain asymmetries in 15,847 people worldwide reveal effects of age and sex. \emph{Brain Imaging and Behavior}, \emph{11}(5), 1497--1514. DOI:~\href{https://doi.org/10.1007/s11682-016-9629-z}{10.1007/s11682-016-9629-z}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=27738994}{27738994}.
\item Yao, N., Winkler, A. M., Barrett, J., Book, G. A., Beetham, T., Horseman, R., Leach, O., Hodgson, K., Knowles, E. E., \textbf{Mathias, S.}, Stevens, M. C., Assaf, M., van Erp, T. G. M., Pearlson, G. D., \& Glahn, D. C. (2017). Inferring pathobiology from structural MRI in schizophrenia and bipolar disorder: modeling head motion and neuroanatomical specificity. \emph{Human Brain Mapping}, \emph{38}(8), 3757--3770. DOI:~\href{https://doi.org/10.1016/s0196-0644(99)70196-4}{10.1016/s0196-0644(99)70196-4}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=28480992}{28480992}.
\item \textbf{Mathias, S. R.}, Knowles, E. E. M., Barrett, J., Leach, O., Buccheri, S., Beetham, T., Blangero, J., Poldrack, R. A., \& Glahn, D. C. (2017). The processing-speed impairment in psychosis is more than just accelerated aging. \emph{Schizophrenia Bulletin}, \emph{43}(4), 814--823. DOI:~\href{https://doi.org/10.1093/schbul/sbw168}{10.1093/schbul/sbw168}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=28062652}{28062652}.
\item Knowles, E. E. M., Huynh, K., Meikle, P. J., Göring, H. H. H., Olvera, R. L., \textbf{Mathias, S. R.}, Duggirala, R., Almasy, L., Blangero, J., Curran, J. E., \& Glahn, D. C. (2017). The lipidome in major depressive disorder: shared genetic influence for ether-phosphatidylcholines, a plasma-based phenotype related to inflammation, and disease risk. \emph{European Psychiatry}, \emph{43}, 44--50. DOI:~\href{https://doi.org/10.1016/j.eurpsy.2017.02.479}{10.1016/j.eurpsy.2017.02.479}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=28365467}{28365467}.
\item Hodgson, K., Carless, M. A., Kulkarni, H., Curran, J. E., Sprooten, E., Knowles, E. E., \textbf{Mathias, S.}, Göring, H. H. H., Yao, N., Olvera, R. L., Fox, P. T., Almasy, L., Duggirala, R., Blangero, J., \& Glahn, D. C. (2017). Epigenetic age acceleration assessed with human white-matter images. \emph{The Journal of Neuroscience}, \emph{37}(18), 4735--4743. DOI:~\href{https://doi.org/10.1523/JNEUROSCI.0177-17.2017}{10.1523/JNEUROSCI.0177-17.2017}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=28385874}{28385874}.
\item Varghese, L., \textbf{Mathias, S. R.}, Bensussen, S., Chou, K., Goldberg, H. R., Sun, Y., Sekuler, R., \& Shinn-Cunningham, B. G. (2017). Bi-directional audiovisual influences on temporal modulation discrimination. \emph{The Journal of the Acoustical Society of America}, \emph{141}(4), 2474. DOI:~\href{https://doi.org/10.1121/1.4979470}{10.1121/1.4979470}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=28464677}{28464677}.
\item Knowles, E. E., Meikle, P. J., Huynh, K., Göring, H. H., Olvera, R. L., \textbf{Mathias, S. R.}, Duggirala, R., Almasy, L., Blangero, J., Curran, J. E., \& Glahn, D. C. (2017). Serum phosphatidylinositol as a biomarker for bipolar disorder liability. \emph{Bipolar Disorders}, \emph{19}(2), 107--115. DOI:~\href{https://doi.org/10.1111/bdi.12468}{10.1111/bdi.12468}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=28230325}{28230325}.
\item Kreitewolf, J., \textbf{Mathias, S. R.}, \& von Kriegstein, K. (2017). Implicit talker training improves comprehension of auditory speech in noise. \emph{Frontiers in Psychology}, \emph{8}, 1584. DOI:~\href{https://doi.org/10.3389/fpsyg.2017.01584}{10.3389/fpsyg.2017.01584}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=28959226}{28959226}.
\item Sprooten, E., Barrett, J., McKay, D. R., Knowles, E. E., \textbf{Mathias, S. R.}, Winkler, A. M., Brumbaugh, M. S., Landau, S., Cyr, L., Kochunov, P., \& Glahn, D. C. (2016). A comprehensive tractography study of patients with bipolar disorder and their unaffected siblings. \emph{Human Brain Mapping}, \emph{37}(10), 3474--3485. DOI:~\href{https://doi.org/10.1002/hbm.23253}{10.1002/hbm.23253}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=27198848}{27198848}.
\item \textbf{Mathias, S. R.} (2016). Unified analysis of accuracy and reaction times via models of decision making. \emph{Proceedings of Meetings on Acoustics}, \emph{26}(1), 050001. DOI:~\href{https://doi.org/10.1121/2.0000219}{10.1121/2.0000219}.
\item Knowles, E. E., Kent, J. W. Jr, McKay, D. R., Sprooten, E., \textbf{Mathias, S. R.}, Curran, J. E., Carless, M. A., de Almeida, M. A., Harald, H. H., Dyer, T. D., Olvera, R. L., Fox, P. T., Duggirala, R., Almasy, L., Blangero, J., \& Glahn, D. C. (2016). Genome-wide linkage on chromosome 10q26 for a dimensional scale of major depression. \emph{Journal of Affective Disorders}, \emph{191}, 123--131. DOI:~\href{https://doi.org/10.1016/j.jad.2015.11.012}{10.1016/j.jad.2015.11.012}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=26655122}{26655122}.
\item \textbf{Mathias, S. R.}, Knowles, E. E., Kent, J. W. Jr, McKay, D. R., Curran, J. E., de Almeida, M. A., Dyer, T. D., Göring, H. H., Olvera, R. L., Duggirala, R., Fox, P. T., Almasy, L., Blangero, J., \& Glahn, D. C. (2016). Recurrent major depression and right hippocampal volume: A bivariate linkage and association study. \emph{Human Brain Mapping}, \emph{37}(1), 191--202. DOI:~\href{https://doi.org/10.1002/hbm.23025}{10.1002/hbm.23025}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=26485182}{26485182}.
\item Glahn, D. C., Knowles, E. E., \textbf{Mathias, S. R.}, Almasy, L., Hodgson, K., Yao, N., Olvera, R. L., Curran, J. E., \& Blangero, J. (2016). Conceptualizing major depression: from genes to neuroanatomy to epidemiology. In T. Lehner, B. L. Miller \& M. W. State (Eds.) \emph{Genomics, circuits, and pathways in clinical neuropsychiatry} (pp.~487--501). Cambridge, MA: Academic Press. DOI:~\href{https://doi.org/10.1016/B978-0-12-800105-9.00031-7}{10.1016/B978-0-12-800105-9.00031-7}.
\item Sprooten, E., Gupta, C. N., Knowles, E. E., McKay, D. R., \textbf{Mathias, S. R.}, Curran, J. E., Kent, J. W. Jr, Carless, M. A., Almeida, M. A., Dyer, T. D., Göring, H. H., Olvera, R. L., Kochunov, P., Fox, P. T., Duggirala, R., Almasy, L., Calhoun, V. D., Blangero, J., Turner, J. A., \& Glahn, D. C. (2015). Genome-wide significant linkage of schizophrenia-related neuroanatomical trait to 12q24. \emph{American Journal of Medical Genetics: Part B, Neuropsychiatric Genetics}, \emph{168}(8), 678--686. DOI:~\href{https://doi.org/10.1002/ajmg.b.32360}{10.1002/ajmg.b.32360}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=26440917}{26440917}.
\item Glahn, D. C., Williams, J. T., McKay, D. R., Knowles, E. E., Sprooten, E., \textbf{Mathias, S. R.}, Curran, J. E., Kent, J. W. Jr, Carless, M. A., Göring, H. H., Dyer, T. D., Woolsey, M. D., Winkler, A. M., Olvera, R. L., Kochunov, P., Fox, P. T., Duggirala, R., Almasy, L., \& Blangero, J. (2015). Discovering schizophrenia endophenotypes in randomly ascertained pedigrees. \emph{Biological Psychiatry}, \emph{77}(1), 75--83. DOI:~\href{https://doi.org/10.1016/j.biopsych.2014.06.027}{10.1016/j.biopsych.2014.06.027}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=25168609}{25168609}.
\item Glahn, D. C., Sprooten, E., Knowles, E. E., McKay, D. R., \textbf{Mathias, S. R.}, Almasy, L., \& Blangero, J. (2015). Imaging genetics. In A. W. Toga, R. A. Poldrack (Eds.) \emph{Brain mapping: An encyclopedic reference} (vol.~3, pp.~929--932). Cambridge, MA: Academic Press. DOI:~\href{https://doi.org/10.1016/B978-0-12-397025-1.00112-3}{10.1016/B978-0-12-397025-1.00112-3}.
\item Knowles, E. E., \textbf{Mathias, S. R.}, McKay, D. R., Sprooten, E., Blangero, J., Almasy, L., \& Glahn, D. C. (2014). Genome-wide analyses of working-memory ability: A review. \emph{Current Behavioral Neuroscience Reports}, \emph{1}(4), 224--233. DOI:~\href{https://doi.org/10.1007/s40473-014-0028-8}{10.1007/s40473-014-0028-8}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=25729637}{25729637}.
\item Roswandowitz, C., \textbf{Mathias, S. R.}, Hintz, F., Kreitewolf, J., Schelinski, S., \& von Kriegstein, K. (2014). Two cases of selective developmental voice-recognition impairments. \emph{Current Biology}, \emph{24}(19), 2348--2353. DOI:~\href{https://doi.org/10.1016/j.cub.2014.08.048}{10.1016/j.cub.2014.08.048}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=25264258}{25264258}.
\item \textbf{Mathias, S. R.} \& von Kriegstein, K. (2014). Percepts, not acoustic properties, are the units of auditory short-term memory. \emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{40}(2), 445--450. DOI:~\href{https://doi.org/10.1037/a0034890}{10.1037/a0034890}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=24188404}{24188404}.
\item \textbf{Mathias, S. R.} \& von Kriegstein, K. (2014). How do we recognise who is speaking? \emph{Frontiers in Bioscience (Scholar Edition)}, \emph{6}, 92--109. DOI:~\href{https://doi.org/10.2741/S417}{10.2741/S417}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=24389264}{24389264}.
\item \textbf{Mathias, S. R.}, Bailey, P. J., Semal, C., \& Demany, L. (2011). A note about insensitivity to pitch-change direction. \emph{The Journal of the Acoustical Society of America}, \emph{130}(4), EL129--EL134. DOI:~\href{https://doi.org/10.1121/1.3629139}{10.1121/1.3629139}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=21974481}{21974481}.
\item \textbf{Mathias, S. R.}, Micheyl, C., \& Bailey, P. J. (2010). Stimulus uncertainty and insensitivity to pitch-change direction. \emph{The Journal of the Acoustical Society of America}, \emph{127}(5), 3026--3037. DOI:~\href{https://doi.org/10.1121/1.3365252}{10.1121/1.3365252}. PMID:~\href{https://www.ncbi.nlm.nih.gov/pubmed/?term=21117752}{21117752}.



\end{bibsection}

\section{Oral Presentations}
\begin{bibsection}

\item \textbf{Mathias, S. R.}, Knowles, E. E. M., Barrett, J., Leach, O., Buccheri S., Beetham, T., Blangero, J., Poldrack, R. A. \& Glahn, D. C. (2017). The processing-speed impairment in psychosis is more than just accelerated aging. Podium presentation at the 72nd \emph{Society of Biological Psychiatry Annual Scientific Program and Convention}, San Diego, CA.

\item \textbf{Mathias, S.~R.}, (2016). Unified analysis of accuracy and reaction times (RTs) via models of decision making. Workshop presentation at the 171st \emph{Meeting of the Acoustical Society of America}, Salt Lake City, UT.

\item \textbf{Mathias, S.~R.}, Shinn-Cunningham, B.~G., Micheyl, C., \& Oxenham, A.~J. (2014). Adaptation reveals automatic pitch-shift detectors in the human auditory system. Podium presentation at the 167th \emph{Meeting of the Acoustical Society of America}, Providence, RI.

\item \textbf{Mathias, S.~R.}, Micheyl, C., \& Shinn-Cunningham, B.~G. (2014). Auditory and visual short-term memories are forgotten differently. Podium presentation at the 37th \emph{Annual Midwinter Research Meeting of the Association for Research in Otolaryngology}, San Diego, CA.
\\\end{bibsection}

%\section{Poster Presentations (excl. coauthored)} \begin{bibsection}

%\item \textbf{Mathias, S.~R.}, Knowles, E.~E.~M, Kent, J.~W., McKay,  D.~R., Curran J.~E, Almeida, M.~A., Dyer, T.~D., G\"oring, H.~H., Olvera, R.~L., Duggirala, R., Fox, P.~T., Almasy, L., Blangero, J. \& Glahn, D.~C. (2015). Recurrent major depression and right hippocampal volume: A bivariate linkage and association study. Poster presentation at the \emph{Society of Biological Psychiatry 71st Annual Meeting}, Atlanta, GA.
%\item \textbf{Mathias, S.~R.}, Knowles, E.~E.~M, Kent, J.~W., McKay,  D.~R., Curran J.~E, Almeida, M.~A., Dyer, T.~D., G\"oring, H.~H., Olvera, R.~L., Duggirala, R., Fox, P.~T., Almasy, L., Blangero, J. \& Glahn, D.~C. (2015). Recurrent major depression and right hippocampal volume: A bivariate linkage and association study. Poster presentation at the \emph{American Society of Human Genetics Annual Meeting}, Baltimore, MD.
%\item \textbf{Mathias, S.~R.}, Micheyl, C., \& Shinn-Cunningham, B.~G. (2014). Gradual decay of auditory short-term memory. Poster presentation at the 167th \emph{Meeting of the Acoustical Society of America}, Providence, RI.
%\item \textbf{Mathias, S.~R.}, Micheyl, C., \& Shinn-Cunningham, B.~G. (2014). Do normal-reading listeners use `perceptual anchors' during frequency-discrimination tasks? Poster presentation at the 167th \emph{Meeting of the Acoustical Society of America}, Providence, RI.
%\item \textbf{Mathias, S.~R.}, Micheyl, C., \& Oxenham, A.~J. (2013). The effect of preceding tones of frequency discrimination. Poster presentation at the 36th \emph{Annual Midwinter Research Meeting of the Association for Research in Otolaryngology}, Baltimore, MD.
%\item \textbf{Mathias, S.~R.}, Micheyl, C., \& Bailey, P.~J. (2010). Insensitivity to pitch-change direction with fixed- And roved-frequency tones. Poster presentation at the 33rd \emph{Annual Midwinter Research Meeting of the Association for Research in Otolaryngology}, Anaheim, CA.
%\item \textbf{Mathias, S.~R.}, \& Bailey, P.~J. (2009). Pitch discrimination with roved- and fixed-frequency stimuli. Poster presentation at the \emph{Short Papers Meeting of the British Society of Audiology}, Southampton.
%\item \textbf{Mathias, S.~R.}, \& Bailey, P.~J. (2008). Insensitivity to the direction of pitch change: The role of stimulus uncertainty and correlations with self-reported hearing. Poster presentation at the \emph{Short Papers Meeting of the British Society of Audiology}, York.
%\item Summerfield, A.~Q., Mathias, S.~R., Knowles, E.~E.~M., Kitterick, P.~T., \& Bailey, P.~J. (2008). Cortical Indices of Auditory Segregation Revealed by Magnetoencephalography: A Parametric Study of Onset Asynchrony and Mistuning. Poster presentation at the 31st \emph{\href{http://www.aro.org/mwm/Program_Book_08_Final_PDF1.pdf}{Annual Midwinter Research Meeting of the Association for Research in Otolaryngology}}, Phoenix, AZ.
%\item \textbf{Mathias, S.~R.}, Knowles, E.~E.~M., Kitterick, P.~T., Bailey, P.~J., \& Summerfield, A.~Q. (2007) Cortical indices of auditory segregation revealed by magnetoencephalography. Poster presentation at the \emph{Short Papers Meeting of the British Society of Audiology}, London.\\
%\end{bibsection}

\section{Reviewer for Journals}
\emph{The Journal of the Acoustical Society of America}\\
\emph{The Journal of Neuroscience}\\
\emph{Perception}\\
\emph{Psychological Medicine}\\
\emph{Psychomusicology}\\
\emph{Schizophrenia Research}\\
\emph{Speech Communication}


\section{Skills}
\begin{bibsection}

\item Statistics\\
I am skilled in statistical methods, particularly Bayesian statistics. Several of my recent papers are ``purely Bayesian,'' containing few or no $p$-values (Mathias et al., 2020a, 2020c).

\item Genetics\\
I am skilled in human quantitative genetics, particularly variance components-based methods that exploit the genetic similarity between individuals. Such methods allow estimation of heritability and genetic correlations (Mathias et al., 2020b), univariate and multivariate linkage, and genome-wide association in related people (Mathias et al., 2016). I regularly contribute to genetics consortia projects (Grasby et al., 2020).

\item Psychophysics and cognitive modeling\\
I am skilled in human psychophysics (Mathias et al., 2010, 2011, 2014, 2017, 2018, 2020a, 2020c) and in developing and fitting models to explain performance in behavioral tasks. I have applied such models to both human (Mathias et al., 2017, 2018, 2020a, 2020c) and rodent (Groman et al., 2019a, 2019b) psychophysical data.

\item Neuroimaging\\
I am accomplished in structural magnetic resonance imaging (MRI) data analysis (Mathias et al., 2016, 2020b) as well as functional magneto/electroencephalography (M/EEG) data analysis (currently unpublished). I regularly perform such analyses to generate quantitative traits for others to use in their genetics studies (Alexander-Bloch et al. 2019; Guadalupe et al., 2017; Kong et al., 2018).

\item Programming\\
I am proficient in several programming languages, most notably \href{https://www.python.org/}{Python}, and to a lesser extent \href{https://www.mathworks.com/products/matlab.html}{MATLAB}/\href{https://www.gnu.org/software/octave/}{Octave}, \href{https://www.r-project.org/}{R}, \href{https://julialang.org/}{Julia}, \href{https://golang.org/}{Go}, and \href{https://mc-stan.org/}{Stan}. I perform most of my statistical analysis using Python and use \href{https://docs.pymc.io/}{PyMC3} for Bayesian inference. Most of my genetics analysis is performed using \href{https://hpc.nih.gov/docs/solar-8.1.1/00.contents.html}{SOLAR}. This CV was written in \href{https://www.latex-project.org/}{\LaTeX}. My most notable programming accomplishment is \href{https://github.com/sammosummo/Charlie2}{Charlie}, a comprehensive neurocognitive test battery and platform for rapid cognitive test development written in Python and \href{https://www.qt.io/}{Qt}. Version 2 is publicly available and open source, while version 3 is currently private but available upon request. Charlie has been used in several previous studies (Koenis et al., 2020; Mathias et al., 2017, 2018; Mollon et al., 2019) and is currently being used for data collection in several ongoing studies.

\end{bibsection}

\section{Teaching}
\begin{bibsection}
\item Website\\
I maintain a \href{https://crackedbassoon.com}{personal website} where I regularly post tutorials on programming and statistical problems.
\item Courses\\
I teach two lectures per year on statistics and quantitative psychology as part of the Neuropsychiatric Genetics Program at Boston Children’s Hospital.
\item Supervision experience
\begin{outerlist}
\item[]Carol Abedelnour (undergraduate) \hfill{2020 -- present}
\begin{innerlist}\item Carol is a Psychology and Neuroscience double major at Emmanuel College. I am currently supervising her undergraduate project  comparing pen-and-paper and computerized versions of the trail-making test.\end{innerlist}
\item[]Josephine Mollon (postdoc)\hfill{2018 -- present}
\begin{innerlist}\item Jo is a postdoc in our lab. I trained Jo to use the computing clusters and perform variance components analysis in SOLAR. I also wrote part of the methods section (the portion concerning variance components analysis) of her paper (Mollon et al., 2018).\end{innerlist}
\item[]Leonard Varghese (PhD student) \hfill{2012 -- 2014}
\begin{innerlist}\item Lenny was a PhD student while I was a postdoc at BU. I trained Lenny to apply the drift-diffusion model and perform Bayesian data analysis in one of his studies, resulting in a paper in \emph{JASA} (Varghese et al., 2017).\end{innerlist}
\item[]Jens Kreitewolf (PhD student/postdoc) \hfill{2012 -- present}
\begin{innerlist}\item Jens was a PhD student while I was a postdoc at the MPI, during which time we worked together on a research project. This collaboration resulted in a paper in \emph{Frontiers} (Kreitewolf et al., 2017). Later Jens was awarded a studentship for a six-month placement in a lab in Montreal. I collaborated with Jens to design the study he conducted during this time, which resulted in a \emph{JASA} paper (Kreitewolf et al., 2018). I continue to collaborate with Jens on various projects.\end{innerlist}
\item[]Carolin Otto (Masters student)  \hfill{2012}
\begin{innerlist}\item I mentored Carolin's Masters project at the MPI.\end{innerlist}
\item[]Gregor Däubler and Denis Gutmann (research assistants) \hfill{2011}
\begin{innerlist}\item Gregor and Denis worked for me as research assistants at the MPI.
\end{innerlist}
\end{outerlist}
%\begin{outerlist}
%\item[]Denis Gutmann, 2011 -- 2012 (Research Assistant)
%\item[]Gregor Däubler, 2012 (Research Assistant)
%\item[]Carolin Otto, 2012 (Masters student)
%\end{outerlist}
%\item Colleagues to whom I have provided considerable assistance, resulting in co-authored publications:
%\begin{outerlist}


%\item[]Jens Kreitewolf
%\item[]Claudia Roswandowtz
%\item[]Leonard Varghese
%\item[]Josephine Mollon
%\item[]Amanda Rodrigue 
%\end{outerlist}
%\item.
\end{bibsection}

\section{Ongoing Research (as PI)}
\begin{bibsection}
\item \href{http://www.childrenshospital.org/research/centers-departmental-programs/tommy-fuss-center}{Tommy Fuss Center}
\begin{outerlist}
\item[] Young Investigator Award \hfill{Oct. 2020 -- Sep. 2022}
\begin{innerlist}
\item \emph{Brain-Age Prediction as a Window into Neurodevelopment in Young People with Psychiatric Disorders}
\item PI: Samuel R. Mathias
\item This project will apply machine learning to archival neuroimaging data from $\sim16,000$ children and young people to develop a ``neurodevelopmental index'' (NI) and will test the hypothesis that NI is related to psychiatric diagnoses and subthreshold variation in pediatric psychiatric symptoms.
\end{innerlist}
\end{outerlist}
\end{bibsection}


\section{Ongoing Research (non-PI role)}
\begin{bibsection}
 \item \href{https://www.nia.nih.gov/}{National Institute on Aging}
\begin{outerlist}
\item[] R01AG058464 \hfill{Aug. 2018 -- May 2023}
\begin{innerlist}
\item \emph{Imaging Genomics of The Aging Brain}
\item PIs: David C.~Glahn, John Blangero
\item The biological mechanisms responsible for age-related changes in neuroanatomy, neurophysiology and neurocognition are largely unknown. By identifying genetic and environmental factors involved in brain aging, our study will reveal novel biological candidates for the determinants of normal aging.
\end{innerlist}
\end{outerlist}

\item \href{http://www.childrenshospital.org/research/centers-departmental-programs/tommy-fuss-center}{Tommy Fuss Center}
\begin{outerlist}
\item[] Next Generation Award \hfill{Sep. 2019 -- Nov. 2024}
\begin{innerlist}
\item \emph{Early Psychosis Investigation (EPI) Center}
\item PI: David C.~Glahn
\item The newly founded EPI center aims to study and treat children and adolescents with early onset psychotic symptoms and their close relatives.
\end{innerlist}
\end{outerlist}
\end{bibsection}

\section{Referees}
%
%\newlength{\rcollength}\setlength{\rcollength}{2.5in}%
%
David C.~Glahn\\
Director, Tommy Fuss Center for Neuropsychiatric Disease Research\\
Boston Children’s Hospital; and\\
Member of the Faculty, Department of Psychiatry\\
Harvard Medical School\\
1 Autumn Street, BCH 3428\\
Boston, MA 02115\\
\textit{Phone:} +1 (617) 919 6819\\
\textit{E-mail:} \href{mailto:david.glahn@childrens.harvard.edu}{david.glahn@childrens.harvard.edu} \\
\\
John Blangero \\
Director, Genomics Computing Center \\
UTRGV School of Medicine \\
South Texas Diabetes and Obesity Insititute \\
Brownsville Campus, BROBL, Room 131 \\
1 West University Blvd \\
Brownsville, TX 78520 \\
\textit{Phone:} +1 (956) 882 7522 \\
\textit{E-mail:} \href{mailto:john.blangero@utrgv.edu}{john.blangero@utrgv.edu} \\
\\
Prof.~Barbara G.~Shinn-Cunningham\\
Director, Carnegie Mellon Neuroscience Institute\\
Baker Hall, 254G\\
Carnegie Mellon University\\
5000 Forbes Avenue\\
Pittsburgh, PA 15213\\
\textit{E-mail:} \href{mailtobgsc@andrew.cmu.edu}{bgsc@andrew.cmu.edu}\\

\end{document}




